\label{cap1_introducao} % Label para referenciar

% Computers and machines easily perform tasks that can be described using formal and mathematical rules.
% However, some trivial activities for human-beings, but difficult to describe formally, are a challenge for them.
% In the last few years, tasks of this latter group, such as object recognition, decision making and speech understanding also began to be performed by software, using machine learning techniques \cite[Ch. 1]{Goodfellow2016}.

% In computer vision, machines can detect objects and edges, identify patterns and segment regions.
% Although some computer vision reached or exceed human capabilities, research is still evolving.
% There is still room for improving techniques and solving practical problems \cite{Khan:2020}.
%This work aims to contribute to the improvement of methods of edge detection and region segmentation, using deep learning techniques.

%--------------------------------
% \subsection{Context and Motivation}
% \label{cap1_motivacao}

% Traditional segmentation methods use basic image properties to find discontinuities that can indicate objects, regions or borders.
% However, these techniques face practical problems, such as similar color patterns, noise, and multiple thresholds for groups of images.
% More recent techniques propose supervised methods using neural networks for edge detection and region segmentation, in which image characteristics are learned by algorithms \cite{MARTIN:1273918} \cite{Segnet:2017:7803544}.
%This approach reduces the need for manual pattern recognition, leaving this task to software \cite{MARTIN:1273918} \cite{Segnet:2017:7803544}.

% In recent years, new practical applications have started to be proposed, such as disease detection in imaging exams, recognition of objects, vehicles, and fire outbreaks in aerial images, and segmentation of images for autonomous vehicles.
% These applications seek to improve performance and lower health care costs, map structures in aerial photographs, ensure environmental maintenance and prevent automotive accidents, providing better quality of life for people \cite{Akkus:2017}, \cite{Kumar:2020}, \cite{Pham:2020}, \cite{Wu:2018}.

% The methods that exist today, despite the greater precision compared to some years ago, can be improved to allow total reliability in automatic systems.
% Medical diagnoses, in the future, can be analyzed entirely by algorithms; plantation can be monitored by software to prevent fires; and autonomous vehicles can become the safest way to go from one place to another.
% Thus, machine and deep learning researches are needed so that these activities can be carried out entirely by software.
%--------------------------------

%--------------------------------
%DEFINIÇÃO DO PROBLEMA
% \subsection{Problem Definition}
% \label{cap1_def_problema}

%Segmentation subdivides an image into its constituent regions or objects, while edge detection techniques identify the boundaries between objects \cite{gonzalez2002digital}.

Image segmentation corresponds to the partition of an image into a set of meaningful areas, while edge detection techniques identify the boundaries between objects, that borders the regions \cite{Dominguez:2016} \cite{gonzalez2002digital}.
Both can be considered as challenging semantic tasks, aiming to determine and group uniform regions for analysis, or identifying pixels that limit those regions.

Edge detection and image segmentation are still active topics of research \cite{Khan:2020} \cite{Sun:2022}, with room for improving techniques and solving practical problems.
As complementary tasks, both can be modeled on each other by sharing effective techniques.

{\color{red}
Edge detection may be subdivided into boundary detection and the classical edge detection, where edge is ``an abrupt change in some low-level image feature such as brightness or color'' while boundary is a contour that represents a change in pixel ownership, that links edges and representation of region boundaries \cite{MARTIN:1273918} \cite{Jain:1995}.
Closed contours represents region boundaries and open contours are parts of region boundaries \cite{Jain:1995}.
% Closed contours represents region boundaries and open contours are parts of region boundaries \cite{Jain:1995}.
% Contours can be combined into a UCM representation, an indexed hierarchy of regions as a soft boundaries \cite{Arbelaez:2006}.
}

According to~\cite{Dominguez:2016}, a proper segmented image should present some fundamental characteristics, such as: (i) region uniformity and homogeneity in  its features, such as gray level, color or texture; (ii) region continuity, without holes; (iii) significant difference between adjacent regions; and (iv) spatial accuracy with smooth and well-defined boundaries.
It could be divided in two stages~\cite{Guigues:2006}: (i) low-level analysis, which evaluates the pixel characteristics, neighboring relation and it is ideally uncommitted in terms of position, orientation, size and contrast; and (ii) high-level analysis, which maps the low-level characteristics to fulfill the task.

Traditional segmentation methods use basic image properties to find discontinuities that can indicate objects, regions or borders.
However, these techniques face practical problems, such as similar color patterns, noise, and multiple thresholds for groups of images \cite{MARTIN:1273918} \cite{Segnet:2017:7803544}.
Recently, deep learning approaches have drastically changed the computational paradigm for visual tasks. The main advantage of deep learning algorithms is that they do not require an engineered model to operate, meaning that they can not only learn the features to represent the data, but also the models to describe them~\cite{Goodfellow:2016}.

Facing deep learning paradigm, hand-crafted features used in the low-level analysis were first replaced by the features learned in deep models~\cite{Farabet:2013, VGGNET:2014, Lee:2015}, which mostly achieved the desirable results.
Due to their architectures, a common CNN produces different information along its layers.
Each layer contributes specifically to the final result, with its own characteristics, that indicates how weights are adjusted by the network.
Furthermore, the network produces information in different sizes along the layers, due convolutional and pooling operations \cite{VGGNET:2014, Zeiler:2014, Fidler:2007, Hadji:2018}. %, that can be combined to produce a single output.

Recently, many proposals explored the learned model for the high-level analysis, in order to create segmentation maps from the outputs of different layers of a deep network~\cite{Xie:2017:HED:3158436.3158453, Cheng:2016, COB:2016, RCF:2017:8100105, Yang:2018}.
These outputs are network samples, which do not require architectural changes and are therefore often called \textit{side-outputs}.
One challenge on the latter strategy is the combination of the side-outputs from distinct layers, considering that they have different sizes and could represent different aspects of the input.

In this work, we propose some strategies to combine the side-outputs from different layers by using simple merging functions in order to explore useful behavior in the learning process.
We also study the amount of combined side-outputs that is needed to create a viable region propositions.
To evaluate our model, the networks were trained for a road image segmentation and edge detection tasks.

In road segmentation, the goal is develop methods to improve Vision-based Driver-Assistance Systems (VB-DAS), that become popular in modern vehicles.
These systems aims to identify lane lines, provide blind spot supervision, and, recently, distinguish the road from different objects such pedestrians, sidewalks and other vehicles \cite{Saleem:2018, Yang:2018, Rezaei:2017}.

Road identification can also be used in road monitoring, traffic management and self-driving cars.
Edge detection task can be use to refine results of region segmentation, refining and improving results.
Also, it is suitable for real-time applications, as microscope images information extraction and road boundary detection \cite{Qu:2020, Li:2020, Perng:2020}

{\color{red}
% In region segmentation task, we adressed the usage of a post-processing filtering based on mathematical morphology idempotent functions~\cite{Najman:2013} in order to remove some undesirable small segments.
% In edge detection, we analyzed how to combine multiple ground truths annotations, presented in some data sets, into a single reference map to increase network convergence.

% Segmentation subdivides an image into its constituent regions or objects, while edge detection techniques identify the boundaries between objects \cite{gonzalez2002digital}.
% An edge, according to \cite{gonzalez2002digital}, is defined as a set of connected pixels that border two regions.

% Region segmentation, object and boundary detection are correlated tasks.
% Object limits with its high-level information can be used to define boundaries location.
% Also, boundaries can limit pixels into regions \cite{MARTIN:1273918}.
% This correlation allows one problem to be modeled on another and effective techniques can be shared between them.

% In order to combine these information at scale, some works such as HED, RCF and BDCN trained convolutional blocks individually, with specific loss functions for each of them.
% This procedure aims to produce macro and detailed information, which are later combined into a single map \cite{Xie:2017:HED:3158436.3158453, RCF:2019, He:2019}.
%This option, however, does not take advantage of existing similar tasks and results, once force several layers to produce the same result, increasing training cost.

% This work seeks to simplify this idea, proposing and evaluating some simple network architectures, based in some recent papers.
% Also, it will be evaluate the capacity of obtain good results without forcing layers to produce similar information.
%This approach allows the information from a model for a specific task (e.g. region segmentation) to be easily adapted, with little training, for a similar task (e.g. edge detection).
%This approach allows to adapt a model for a specific task (e.g. region segmentation) to a similar one (e.g. edge detection).

% To evaluate the methodology, our work will show results obtained in the tasks of region segmentation and edge detection.
% The task of region segmentation was addressed in our previous work \cite{Reis:2019} and, at this stage, we will focus mainly, but not only, in edge detection.
}

In edge detection we will refine the results of our previous work \cite{Reis:2019} in a more difficult task, that will allow to identify more clearly the best technique to combine side-outputs.
Also, this paper will address how to combine multiple ground truths annotations, presented in some data sets, into a single reference map to increase training speed and performance.

%This work also developed generic loss functions and trivial operations to combine side-outputs, such as average, maximum and sum.
%The creation of simple or even trivial methods favors the use in different scenarios.
%--------------------------------
